Fluoroproj: Title to be decided later

### 2023-07-14 manuscript/manuscript.qmd
notes added to manuscript

@@

@@

Stats?  One-to-one lines? Regressions with r2?

@@

@@

```{r read_tabl1, echo=FALSE, message=FALSE}
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) %>%
  select(-family) %>%
  mutate(biovolume = round(biovolume, 1),
         relative_biovolume = round(relative_biovolume, 5))
```

@@

Discuss amongst yourselves.

>>>>

<!-- Look at yellow substance and blank corrections on cyanfluor and in vivo (maybe others).  -->

@@

### Statistical Analysis

Make some comment about why no 1:1 line, using regression and r2 to compare sensors

@@

Stats?  Regressions with r2?

@@

<!-- TODO: Add Regression Lines to plots add R2-->

@@

```{r read_table1, echo=FALSE, message=FALSE}
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) %>%
  select(-family) %>%
  mutate(biovolume = round(biovolume, 1),
         relative_biovolume = round(relative_biovolume, 5))
```

@@

Chlorophyll is not so good in some cases, but can be explained by phytoplankton community distributions

Phycocyanin is good

Don't read anything into absolute values (i.e. chlorophyll from one sensor not equal to chlorophyll from another sensor) across sensors, but general patterns are still very useful

Phycocyanin very good proxy for cell counts. Suggest replacing cell counts for waterbody listing decisions with phycocyanin. Would likely need additional work to furhter explore relationship, build predictive models of cell coutns, etc.
